\chapter*{Lista publikacji}
%\chapter{Lista publikacji}
\thispagestyle{empty}
\pagestyle{empty}

\par
\hspace{0.6cm}C. Zet, H. Kiesewetter, M. Skoczylas, L. Westerberg, R. Spohr. A system for irradiating polymer films with a preset number of ions. GSI Scientific Report, Gesellschaft f\"ur Schwerionenforschung mbH (GSI), 154, 2003

\par
C. Zet, C. Foslau, M. Skoczylas, L. Westerberg, R. Spohr. System for irradiating polymer films with a preset number of ions. SIELMEN, 4th International Conference on Electromechanical and Power Systems  vol. 2, 167-170, 2003

\par M. Skoczylas, K. Andrzejewski. Krzyżtopór. Telewizja Polska, wyd. Rzeczpospolita, Akademia Filmu i Telewizji Warszawa, 2005

\par
R. Spohr, P. Apel, H. Kiesewetter, M. Skoczylas, C. Zet. Elektrolytische Bank. Patent~DE~10~2005~020~734, 2006

\par
M. Skoczylas, R. Cherubini, S. Gerardi. Automatic unstained cells recognition for single-cell irradiations. LNL Annual Report, INFN-LNL, 61-62, 2006

\par
M. Skoczylas, R. Cherubini, S. Gerardi. Automatic unstained cells recognition for single-cell irradiations, Proceedings of the XIII International Congress of Radiation Research, San Francisco, USA, 2007

\par
M. Skoczylas, R. Cherubini, S. Gerardi. Further development of the INFN-LNL automated unstained cell recognition system for single-cell irradiations. LNL Annual Report, INFN-LNL, 2008

\par
M. Skoczylas, R. Cherubini, S. Gerardi. Automated detection system of unstained viable cells in phase-contrast microscopy. Proceedings of the 8th International Workshop on Microbeam probes of cellular radiation response, NIRS, Chiba, Japan, November 13-15, 2008, p. 5-2; Journal of Radiation Research, Vol. 50, Supplement A, A107, 2009

\par
M. Skoczylas, K. Bandurski, R. Cherubini, V. De Nadal, S. Gerardi. On-line results of the INFN-LNL automated unstained cell recognition system for single-cell irradiations. LNL Annual Report, INFN-LNL, 2009

\par
M. Skoczylas, R. Cherubini, S. Gerardi. Automatic detection of unstained viable cells in phase-contrast microscope images. Zeszyty Naukowe Politechniki Bialostockiej, zeszyt 4, 2009

\par
M. Skoczylas, W. Rakowski, R. Cherubini, S. Gerardi. Wavelet-SVM classification and automatic recognition of unstained viable cells in phase-contrast microscopy. Radiation Protection Dosimetry, Oxford Journals, 2010

\par
M. Skoczylas, W. Rakowski, R. Cherubini, S. Gerardi. Unstained viable cell recognition in phase-contrast microscopy. Opto-Electronics Review, Versita, Springer-Verlag~GmbH, 2011
